Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-20 paper/main.tex
finished adding (draft) descriptions of all tasks

\paragraph*{Spatial learning (Fig.~\ref{fig:tasks}d).}

>>>>

\paragraph*{Spatial learning (Fig.~\ref{fig:tasks}d).}
Participants performed a series of study-test trials where they
memorized the onscreen spatial locations of two or more shapes.
During the study phrase of each trial, a set of shapes appeared on the screen for
10~s, followed by 2~s of blank (white) screen.  During the test phase
of each trial, the same shapes appeared onscreen again, but this time
they were vertically aligned and sorted horizontally in a random
order.  Participants were instructed to drag (using the mouse) each
shape to its studied position, and then to click a button to indicate
that the placements were complete.

In different study-test trials, participants learned the locations of
different numbers of shapes (always drawn from the same pool of 7
unique shapes, where each shape appeared at most one time per trial).
They first performed three trials where they learned the locations of
2 shapes; next three trials where they learned the locations of 3
shapes; and so on until their last three trials, where (during each trial) they learned
the locations of 7 shapes.  All told, each participant performed 18
study-test trials of this spatial learning task (3 trials for each of 2, 3,
4, 5, 6, and 7 shapes).
